Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-06-11 vesicle_code/docs/permeableVes/main.tex
updated figures

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/parabolicPhaseDiagram.tikz}
%  \fi
  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and flow rates $U$.}
\end{figure}

@@

\input{figures/shearPhaseDiagramRA2.tikz}

>>>>

\begin{figure}[htp]
%  \ifTikz
%  \input{figures/parabolicPhaseDiagram.tikz}
%  \fi
  \includegraphics[width=0.8\linewidth]{figures/parabolicPhaseDiagram.pdf}
  \caption{\label{fig:parabolicPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and flow rates $U$. At high flow rates, the vesicle
  self-intersects before reaching a steady state configuration.}
\end{figure}

@@

%\input{figures/shearPhaseDiagramRA2.tikz}
%\input{figures/parabolicPhaseDiagram.tikz}
